A Taxonomy of Twists of Supersymmetric Yang--Mills Theories

### 2020-01-27 paper.tex

Next we look at the case of the twist by a rank $(1,2)$ supercharge. As in many cases so far, it will be useful to consider a family of topological supercharges which are generically of rank $(1,2)$.

@@

>>>>

Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.

@@

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4d12hodge}
\end{theorem}
